A holographic approach to the six-dimensional superconformal index

### 2022-10-13 fivebranes/index.tex
br

The existence of a solution to this equation is a strong constraint on the THF manifold $M$. The relevant consequence for us is that it implies the degeneration of the spectral sequence \ref{thfss} at the $E_{2}$-page.

@@

The phase space at $\infty\in \R_{>0}$ is computed by restricting to a neighborhood $(a, \infty)\subset \R_{>0}$:
\beqn
(p| \mathring M)_* \cL_{sugra}|_{\infty \times Z}=
\eeqn

There is a symplectic pairing given by
\beqn
\eeqn

\surya{...}

>>>>

The existence of a solution to this equation is a strong constraint on the THF manifold $M$. The relevant consequence for us is that it implies the degeneration of the spectral sequence \ref{thfss} at the $E_{2}$-page. From this point onwards, we assume that there exists a solution $\gamma_{BR}$ to the above equation.

Accordingly, the dimensional reduction takes the form

\[
\cA^{\bu}_{\R_{>0}\times Z} \otimes \left ( \Pi T^{*} (\cO (\C^{2}) \otimes V) \right)
\]

Deforming by the Maurer-Cartan element turns on a differential given by bracketing with $\thf D\gamma_{BR}$. Thus the theory in the backreacted geometry is given by

\[
\cA^{\bu}_{\R_{>0}\times Z} \otimes \left ( \cO (\C^{2})\otimes V \xrightarrow{D\gamma_{BR}} \Pi (\cO (\C^{2})\otimes V)^{*} \right )
\]

@@

The phase space at $\infty\in \R_{>0}$ is computed by restricting to a neighborhood $(a, \infty)\subset \R_{>0}$:
\beqn
(p| \mathring M)_* \cL_{sugra}|_{\infty \times Z}= \cA^\bullet_Z \otimes
\eeqn

The polarization identified in section
